Estimating the association between Facebook adoption and well-being in 72 countries

### 2022-11-04 ms.Rmd
Prepare for submission

abstract: |
  \textbf{Abstract} Social media's potential effects on well-being have received considerable research interest, but much of past work is hampered by an exclusive focus on demographics in the Global North and inaccurate self-reports of social media engagement. We describe associations linking 72 countries' Facebook adoption to the well-being of 946,798 individuals from 2008 to 2019. We found no evidence suggesting that the global penetration of social media is associated with widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time. The observed associations were small. Facebook adoption predicted well-being more positively for younger individuals, but country-specific results were mixed. To move beyond studying aggregates and to better understand social media's roles in people's lives, and their potential causal effects, we need more transparent collaborative research between independent scientists and the technology industry. \linebreak[4]

  \textbf{Statement of relevance} Billions of individuals across the globe use social media on a regular basis. The widespread adoption of social media---most prominently Facebook---has fundamentally shifted how humans conduct their lives. Consequently, researchers, healthcare professionals, and policy makers have repeatedly raised alarms that the spread of social media may be negatively affecting individuals', particularly young ones', mental health and well-being on a global scale. We examined the plausibility of this idea by associating 72 nations' yearly Facebook adoption rates to the well-being of 946,798 individuals from 2008 to 2019. Overall, we found that increased rates of daily and monthly active Facebook users slightly predicted greater levels of well-being, when comparing countries to other countries, or countries to themselves but over time. These findings should guide debate surrounding social media towards more empirical foundations: The importance of this topic requires that independent scientists gain access to more detailed data from the technology industry in order to better determine how, when, and why modern online platforms might be affecting their users.

keywords: well-being, social media
wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
bibliography: "references.bib"
floatsintext: yes
linenumbers: yes
draft: no
mask: yes
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: doc
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
always_allow_html: true
---

```{r setup, include = FALSE}
# Packages
library(papaja)
library(scales)
library(knitr)
library(patchwork)
library(ggh4x)
library(brms)
library(kableExtra)
library(ggstance)
library(bayestestR)
library(tidyverse)

@@

@@

# Merge
d <- left_join(d_gwp, d_fb) %>% 
  mutate(age = factor(age, levels = c("13-34", "35+")))
```

@@

# Prepare data
dm <- d %>% 
  # Centering predictors
  # Grand mean centering so both components are zero-centered
  mutate(across(c(dau, mau), ~. - mean(., na.rm = TRUE))) %>% 
  group_by(country) %>%
  mutate(
    # Between
    dau_cb = mean(dau, na.rm = TRUE),
    mau_cb = mean(mau, na.rm = TRUE),
    # Within
    dau_cw = dau - dau_cb, 
    mau_cw = mau - mau_cb
  ) %>% 
  ungroup() %>% 
  # Center year so that intercepts are at 2014
  mutate(year = year - 2014) %>% 
  # Remove rows where predictor existed but outcome didn't
  drop_na(val)

# Model formula
model_dau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + dau_cw) * age * sex + dau_cb +
    ((year + dau_cw) * age * sex | country),
  family = gaussian()
)
model_mau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + mau_cw) * age * sex + mau_cb +
    ((year + mau_cw) * age * sex | country),
  family = gaussian()
)
fits <- dm %>% 
  select(outcome, year, country, sex, age, contains("_c"), val, se) %>% 
  group_by(outcome) %>% 
  nest() %>% 
  crossing(
    nesting(
      model = list(model_dau, model_mau),
      predictor = c("dau", "mau")
    )
  ) %>% 
  mutate(
    fit = pmap(
      list(model, data, outcome, predictor),
      ~brm(
        ..1,
        cores = 4, chains = 4,
        backend = "rstan",
        control = list(adapt_delta = .95),
        iter = 3000,
        data = ..2,
        file = str_glue("models/brm-{..3}-{..4}")
      )
    )
  )
```

@@

To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of well-being. We examined 72 countries' per capita active Facebook users in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019. The well-being data represented 946,798 individuals' responses from the nationally representative Gallup World Poll Survey [@gallupHowDoesGallup2014]. We joined these unique datasets to conduct a descriptive study to answer three basic yet important questions: First, to what extent is Facebook adoption associated with well-being? Second, do these associations differ by age or sex. And finally, how might these associations have differed between countries? In addition, we were interested in whether the intensity of use might make a difference, and therefore conducted our analyses separately for daily active users and monthly active users.

@@

Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript. Our analytic code, along with synthetic datasets and an online analysis supplement, is available at <https://doi.org/10.5281/zenodo.7086277>. This study was not preregistered. Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset. The Gallup data are available online to subscribing institutions.

@@

```{r}
# Text list of countries
countries <- sort(unique(d_fb$country))
countries[length(countries)] <- paste("and", countries[length(countries)])
countries <- str_c(countries, collapse = ", ")
```

We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure 2). FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000. We report analyses based on DAU in the main manuscript, and MAU in the online supplement. Facebook calculates DAU and MAU estimates separately for individuals aged 13-34 and 35+. User age is determined based on Facebook profile information, which can be inaccurate (e.g. young users reporting an older age.) Accordingly, Facebook has trimmed 0.008% of total MAU to exclude accounts with unrealistic or non-reported ages.

@@

The NE items are responses to "Did you experience the following feelings during a lot of the day yesterday?" for physical pain, worry, sadness, stress, and anger? For analyses we used the means of these scales. Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top. The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you. On which step of the ladder would you say you personally feel you stand at this time?". For analyses, we scaled these variables to percentages, and aggregated the `r number(gwp_n, big.mark = ",")` individuals’ data to means and standard errors for each country, year, sex, and age (15-34 and 35+) combination (`r number(gwp_n_groups, big.mark = ",")` cells).

@@

p_b <- d %>% 
  # Exclude rows where FB data existed but not GWP data
  drop_na(val) %>% 
  # Actual lowest age in GWP
  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE"
    )
  ) %>% 
  mutate(panel = str_glue("{age} ({sex})")) %>% 
  ggplot(aes(year, val, group = country)) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Value", 
    expand = expansion(.01),
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2),
    labels = ~str_replace(., "20", "'")
  ) +
  geom_line(size = .1) +
  facet_grid(
    outcome~panel, 
    scales = "free_y",
    labeller = as_labeller(~str_replace(., "_", " "))
  )

((p_a / p_b) &
    theme(
      strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
      strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
      text = element_text(size = 5)
    )) +
  plot_layout(heights = c(4, 6)) +
  plot_annotation(tag_levels = "A")
```

@@

Facebook adoption increased markedly from 2008, when the mean per capita DAU across these 72 countries was `r tmp[1,3]` (ages 13-34) and `r tmp[2,3]` (35+), to `r tmp[1,14]` (13-34) and `r tmp[2,14]` (35+; Figure 1A) in 2019. The mean MAUs in 2019 were greater at `r tmp[3, 14]` (13-34) and `r tmp[4, 14]` (35+). During this period Facebook adoption by younger individuals reached near 100% in many countries, but not for older individuals. At the same time, we did not observe correspondingly large and uniform changes across measures of well-being; life satisfaction had remained relatively stable, whereas both negative and positive experiences had slightly increased (Figure 1B) [@vuorreGlobalWellbeingMental2022].

We then focused on our first question: How Facebook adoption relates to well-being in the average country and demographic. We first examined whether and how the relative standing of countries on their average Facebook adoption predicted well-being (between-country associations, $\alpha_{12}$). We found that countries with greater average daily active Facebook users (DAU) had higher levels of life satisfaction and positive experiences, and lower levels of negative experiences, than countries with lower DAU (Table 1; Between countries). However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions [@sprukInstitutionalOriginsSubjective2016]. While descriptively informative, these associations are therefore likely to indicate between-country confounding factors.

@@

# Average within- and between-country associations
tab_world <- coefs %>% 
  filter(
    country == "World",
    Hypothesis %in% c("Average", "Between-country")
  ) %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE"
    )
  ) %>% 
  mutate(
    across(c(Mean, CI_low, CI_high), list("str" = ~number(., .01))),
    result = str_glue(
      "{Mean_str} [{CI_low_str}, {CI_high_str}] ({percent2(pd)})"
    )
  ) %>% 
  select(
    predictor, Outcome = outcome, Hypothesis, result
  ) %>% 
  pivot_wider(names_from = Hypothesis, values_from = result) %>% 
  rename(
    `Within-country` = Average,
    `Between countries` = `Between-country`
  ) %>% 
  select(predictor, Outcome, `Between countries`, `Within-country`) %>% 
  arrange(predictor, Outcome)

tab_world %>% 
  mutate(
    Predictor = str_to_upper(predictor), 
    Predictor = if_else(1:n() %in% c(1, 4), Predictor, ""),
    .keep = "unused", .before = 1
  ) %>% 
  rename(X = Predictor, Y = Outcome) %>% 
  mutate(
    across(
      ends_with("country"), 
      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
    ),
    across(
      ends_with("country"),
      ~str_replace_all(., "%", "\\\\%")
    )
  ) %>% 
  apa_table(
    caption = "Average Facebook adoption and well-being associations",
    font_size = "scriptsize",
    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction).",
    span_text_columns = FALSE,
    escape = FALSE,
    midrules = 3,
    placement = "htb",
    align = 'llll'
  )
```

Variations in such confounding factors are likely to be significantly smaller within countries but over time in a 12-year period. We therefore next focused on the model's within-country associations. They measure the extent to which Facebook adoption in a given country predicted well-being in that country, adjusting for temporal trends in the country's well-being outcome ($\alpha_4$). For the average country and across age and sex, we found that within-country increases in DAU predicted greater levels of life satisfaction and positive experiences, and lower levels of negative experiences, although only the latter association's 95%CI excluded zero (Table 1; Within-country).

@@

```{r}
tmp <- fits %>% 
  select(outcome, predictor, fit) %>% 
  mutate(
    out = map(
      fit,
      ~describe_posterior(
        .x, 
        rope_range = c(-.01, .01), 
        rope_ci = 1,
        parameters = c("_cw$")
      )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out)
tmp <- tmp %>% 
  select(predictor, outcome, ROPE_Percentage) %>% 
  mutate(x = percent2(1 - ROPE_Percentage), .keep = "unused") %>% 
  pivot_wider(names_from = outcome, values_from = x)
tmp
```

In addition to simple sign tests, we quantified evidence for the associations to be greater in magnitude to a 0.01% change as a function of 1% increase in MAU/DAU [@kruschkeBayesianNewStatistics2017]. DAU predicted negative and positive experiences in excess of 0.01% with `r tmp[1,3]` and `r tmp[1, 4]` probability, respectively, and MAU predicted positive experiences in excess of 0.01% with `r tmp[2,4]` probability. In sum, then, for the average country in our sample, Facebook adoption positively predicted well-being. Nevertheless, our certainties in the directions of these associations were not great, and the magnitudes of these associations were small: A one-percent increase in DAU predicted a `r tab_world[3,4]` increase in positive experiences for the average country. While these associations indicate relations within countries and adjust for confounders that vary linearly with time by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations. Rather, this association describes that all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.

```{r demographics}
# Differences between ages
age <- coefs %>% 
  filter(
    Hypothesis == "X by age",
    country == "World"
  ) %>% 
  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
  select(
    Predictor = predictor, Outcome = outcome, result
  ) %>% 
  pivot_wider(names_from = Outcome, values_from = result)

# And sexes
sex <- coefs %>% 
  filter(
    Hypothesis == "X by sex",
    country == "World"
  ) %>% 
  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
  select(
    Predictor = predictor, Outcome = outcome, result
  ) %>% 
  pivot_wider(names_from = Outcome, values_from = result)

@@

We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between age and sex. DAU predicted negative experiences more negatively, and MAU positive experiences more positively, for the younger age group than for the older (`r age[1, 3]`, `r age[2, 4]`). Other average age differences were not credibly different from zero at the 95% level. The association between DAU and MAU and well-being was more positive for males than it was for females, across all well-being measures, but the differences were not credibly different from zero. We display the average age- and sex-specific associations in the bottom row of Figure 2. Overall, these results indicated that the association between Facebook adoption and well-being was more positive for younger individuals, particularly for negative and positive experiences, and that sex-based differences were much smaller in magnitude and not credibly different from zero.

```{r fig-forest}
#| echo: false
#| include: true
#| fig.height: 5.4
#| fig.width: 7
#| out.width: "\\textwidth" 
#| fig.env: "figure*"
#| fig.cap: "Within-country associations between daily (left; DAU) and monthly (right; MAU) active Facebook users and life satisfaction (LS), negative experiences (NE), and positive experiences (PE). Units indicate percentage change in outcome as function of percentage increase in within-country centered DAU or MAU. Filled points indicate estimates whose 95\\%CI excludes zero."
tmp <- coefs %>%   
  filter(
    str_detect(Hypothesis, "_")
  ) %>% 
  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE"
    ),
    predictor = if_else(
      predictor == "dau",
      "Daily active users",
      "Monthly active users"
      )
  ) %>% 
  mutate(cred = pd >= .975)

>>>>

abstract: |
  Social media's potential effects on well-being have received considerable research interest, but much of past work is hampered by an exclusive focus on demographics in the Global North and inaccurate self-reports of social media engagement. We describe associations linking 72 countries' Facebook adoption to the well-being of 946,798 individuals from 2008 to 2019. We found no evidence suggesting that the global penetration of social media is associated with widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time. The observed associations were small. Facebook adoption predicted well-being more positively for younger individuals, but country-specific results were mixed. To move beyond studying aggregates and to better understand social media's roles in people's lives, and their potential causal effects, we need more transparent collaborative research between independent scientists and the technology industry.

keywords: well-being, social media
wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
bibliography: "references.bib"
floatsintext: yes
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: doc
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
always_allow_html: true
---

```{r setup, include = FALSE}
# Packages
library(papaja)
library(scales)
library(knitr)
library(patchwork)
library(ggh4x)
library(kableExtra)
library(ggstance)
library(bayestestR)
library(brms)
library(tidyverse)

@@

# Global burden of disease
d_gbd <- read_rds("data/gbd.rds")

@@

# Merge
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
  )
d <- left_join(
  bind_rows(d_gwp, d_gbd), 
  d_fb
) %>% 
  mutate(
    age = factor(age, levels = c("13-34", "35+")),
    outcome = factor(outcome, levels = oo)
  )
```

@@

# Create centered predictors
# Outcomes can have different countries / years, do by country
d <- d %>% 
  # Grand mean centering so both components are zero-centered
  group_by(outcome) %>% 
  mutate(
    across(
      c(dau, mau), 
      .fns = list(c = ~. - mean(., na.rm = TRUE))
    )
  ) %>% 
  # Outcomes may have different data so do by outcome
  group_by(outcome, country) %>%
  mutate(
    # Between
    dau_cb = mean(dau_c, na.rm = TRUE),
    mau_cb = mean(mau_c, na.rm = TRUE),
    # Within
    dau_cw = dau_c - dau_cb, 
    mau_cw = mau_c - mau_cb
  ) %>% 
  ungroup()

d <- d %>% 
  mutate(sex = factor(sex), age = factor(age))

# Model formula
model_dau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + dau_cw) * age * sex + dau_cb +
    ((year + dau_cw) * age * sex | country),
  family = gaussian()
)
model_mau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + mau_cw) * age * sex + mau_cb +
    ((year + mau_cw) * age * sex | country),
  family = gaussian()
)
fits <- d %>% 
  select(outcome, year, country, sex, age, contains("_c"), val, se) %>% 
  group_by(outcome) %>% 
  nest() %>% 
  crossing(
    nesting(
      model = list(model_dau, model_mau),
      predictor = c("dau", "mau")
    )
  ) %>% 
  mutate(
    fit = pmap(
      list(model, data, outcome, predictor),
      ~brm(
        ..1,
        cores = 4,
        backend = "rstan",
        control = list(adapt_delta = .95),
        iter = 4000,
        # Center year on 2014
        data = mutate(..2, year = year - 2014),
        file = str_glue("models/brm-{..3}-{..4}")
      )
    )
  )
```

```{r diagnostics}
if (length(list.files("diagnostics")) == 0) {
  rhats <- fits %>% 
    mutate(
      out = map(
        fit, 
        ~describe_posterior(
          .x, 
          ci_method = "eti", 
          test = NULL, 
          effects = "all",
          parameters = "^cor_|^sd_|^b_"
        ) %>% 
          as_tibble() %>% 
          select(Parameter, Rhat, ESS)
      )
    ) %>% 
    select(-fit, -data, -model) %>% 
    unnest(out)

  # Show a table of bad rhats
  rhats %>%
    filter(!near(Rhat, 1, tol = .01)) %>% 
    arrange(desc(Rhat))

  # Draw a scatterplot of parameters with 9 worst rhats
  # Create a tabset of this in HTML output
  rhats_sum <- rhats %>% 
    group_by(outcome, predictor) %>% 
    arrange(outcome, predictor, desc(abs(Rhat))) %>% 
    slice(1:9) %>% 
    summarise(v = list(str_c(Parameter))) %>% 
    ungroup() %>% 
    right_join(select(fits, -data, -model))

  dir.create("diagnostics", FALSE)
  for (i in 1:nrow(rhats_sum)) {
    x <- slice(rhats_sum, i)
    path <- str_glue("diagnostics/{x$outcome}-{x$predictor}.png")
    png(path, width = 1200, height = 1200, units = "px", res = 120)
    pairs(x = x$fit[[1]]$fit, pars = x$v[[1]])
    dev.off()

  }
}
```

@@

To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of well-being. We examined 72 countries' per capita active Facebook users in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019. The well-being data represented 946,798 individuals' responses from the nationally representative Gallup World Poll Survey [@gallupHowDoesGallup2014]. We joined these unique datasets to conduct a descriptive study to answer three basic yet important questions: First, to what extent is Facebook adoption associated with well-being? Second, do these associations differ by age or sex. And finally, how might these associations have differed between countries? In addition, we were interested in whether the intensity of use might make a difference, and therefore conducted our analyses separately for daily active users and monthly active users. As a supplementary analysis, we replicated and present these analyses on meta-analytic mental health outcomes in an appendix.

@@

Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript. Our analytic code, along with synthetic datasets, is available at <https://doi.org/10.5281/zenodo.7086277> [@vuorreEstimatingAssociationFacebook2022a]. This study was not preregistered. Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset. The Gallup well-being data are available online to subscribing institutions.

@@

We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure \@ref(fig:fig-forest)). FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000. We report analyses based on DAU in the main manuscript, and MAU in the online supplement. Facebook calculates DAU and MAU estimates separately for individuals aged 13-34 and 35+. User age is determined based on Facebook profile information, which can be inaccurate (e.g. young users reporting an older age.) Accordingly, Facebook has trimmed 0.008% of total MAU to exclude accounts with unrealistic or non-reported ages.

@@

The NE items are responses to "Did you experience the following feelings during a lot of the day yesterday?" for "physical pain", "worry", "sadness", "stress", and "anger". For analyses we used the means of these scales. Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top. The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you. On which step of the ladder would you say you personally feel you stand at this time?". For analyses, we scaled these variables to percentages, and aggregated the `r number(gwp_n, big.mark = ",")` individuals’ data to means and standard errors for each country, year, sex, and age (15-34 and 35+) combination (`r number(gwp_n_groups, big.mark = ",")` cells).

@@

p_b <- d %>% 
  # GWP only
  filter(outcome %in% oo[1:3]) %>% 
  # Exclude rows where FB data existed but not GWP data
  drop_na(val) %>% 
  # Actual lowest age in GWP
  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE"
    )
  ) %>%
  mutate(panel = str_glue("{age} ({sex})")) %>% 
  ggplot(aes(year, val, group = country)) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Value", 
    expand = expansion(.01),
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2),
    labels = ~str_replace(., "20", "'")
  ) +
  geom_line(size = .1) +
  facet_grid(
    outcome~panel, 
    scales = "free_y",
    labeller = as_labeller(~str_replace(., "_", " "))
  )

((p_a / p_b) &
    theme(
      strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
      strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
      text = element_text(size = 7)
    )) +
  plot_layout(heights = c(4, 6)) +
  plot_annotation(tag_levels = "A")
```

@@

Facebook adoption increased markedly from 2008, when the mean per capita DAU across these 72 countries was `r tmp[1,3]` (ages 13-34) and `r tmp[2,3]` (35+), to `r tmp[1,14]` (13-34) and `r tmp[2,14]` (35+; Figure \@ref(fig:fig-data)A) in 2019. The mean MAUs in 2019 were greater at `r tmp[3, 14]` (13-34) and `r tmp[4, 14]` (35+). During this period Facebook adoption by younger individuals reached near 100% in many countries, but not for older individuals. At the same time, we did not observe correspondingly large and uniform changes across measures of well-being; life satisfaction had remained relatively stable, whereas both negative and positive experiences had slightly increased (Figure \@ref(fig:fig-data)B) [@vuorreGlobalWellbeingMental2022].

We then focused on our first question: How Facebook adoption relates to well-being in the average country and demographic. We first examined whether and how the relative standing of countries on their average Facebook adoption predicted well-being (between-country associations, $\alpha_{12}$). We found that countries with greater average daily active Facebook users (DAU) had higher levels of life satisfaction and positive experiences, and lower levels of negative experiences, than countries with lower DAU (Table \@ref(tab:tab-world)); Between countries). However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions [@sprukInstitutionalOriginsSubjective2016]. While descriptively informative, these associations are therefore likely to indicate between-country confounding factors.

@@

# Average within- and between-country associations
tab_world <- coefs %>% 
  filter(
    country == "World",
    Hypothesis %in% c("Average", "Between-country")
  ) %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE",
      TRUE ~ outcome
    )
  ) %>%
  mutate(
    across(c(Mean, CI_low, CI_high), list("str" = ~number(., .01))),
    result = str_glue(
      "{Mean_str} [{CI_low_str}, {CI_high_str}] ({percent2(pd)})"
    )
  ) %>% 
  select(
    predictor, Outcome = outcome, Hypothesis, result
  ) %>% 
  pivot_wider(names_from = Hypothesis, values_from = result) %>% 
  rename(
    `Within-country` = Average,
    `Between countries` = `Between-country`
  ) %>% 
  select(predictor, Outcome, `Between countries`, `Within-country`) %>% 
  arrange(predictor, Outcome)

tab_world %>% 
  filter(Outcome %in% c("LS", "NE", "PE")) %>% 
  mutate(
    Predictor = str_to_upper(predictor), 
    Predictor = if_else(1:n() %in% c(1, 4), Predictor, ""),
    .keep = "unused", .before = 1
  ) %>% 
  rename(X = Predictor, Y = Outcome) %>% 
  mutate(
    across(
      ends_with("country"), 
      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
    ),
    across(
      ends_with("country"),
      ~str_replace_all(., "%", "\\\\%")
    )
  ) %>% 
  apa_table(
    caption = "Average Facebook adoption and well-being associations",
    font_size = "scriptsize",
    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction).",
    span_text_columns = FALSE,
    escape = FALSE,
    midrules = 3,
    placement = "htb",
    align = 'llll'
  )
```

Variations in such confounding factors are likely to be significantly smaller within countries but over time in a 12-year period. We therefore next focused on the model's within-country associations ($\alpha_4$). They measure the extent to which Facebook adoption in a given country predicted well-being in that country, adjusting for temporal trends in the country's well-being outcome. For the average country and across age and sex, we found that within-country increases in DAU predicted greater levels of life satisfaction and positive experiences, and lower levels of negative experiences, although only the latter association's 95%CI excluded zero (Table \@ref(tab:tab-world); Within-country).

@@

```{r}
tmp <- fits %>% 
  filter(outcome %in% oo[1:3]) %>% 
  select(outcome, predictor, fit) %>% 
  mutate(
    out = map(
      fit,
      ~describe_posterior(
        .x, 
        rope_range = c(-.01, .01), 
        rope_ci = 1,
        parameters = c("_cw$")
      )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out)
tmp <- tmp %>% 
  select(predictor, outcome, ROPE_Percentage) %>% 
  mutate(x = percent2(1 - ROPE_Percentage), .keep = "unused") %>% 
  pivot_wider(names_from = outcome, values_from = x)
tmp
```

In addition to sign tests, we quantified evidence for the associations to be greater in magnitude to a 0.01% change as a function of 1% increase in MAU/DAU [@kruschkeBayesianNewStatistics2017]. DAU predicted negative and positive experiences in excess of 0.01% with `r tmp[1,3]` and `r tmp[1, 4]` probability, respectively, and MAU predicted positive experiences in excess of 0.01% with `r tmp[2,4]` probability. In sum, then, for the average country in our sample, Facebook adoption positively predicted well-being. Nevertheless, our certainties in the directions of these associations were not great, and the magnitudes of these associations were small: A one-percent increase in DAU predicted a `r tab_world[3,4]` increase in positive experiences for the average country. While these associations indicate relations within countries and adjust for confounders that vary linearly with time by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations. Rather, this association describes that all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.

```{r demographics}
# Differences between ages
age <- coefs %>% 
  filter(
    outcome %in% oo[1:3],
    Hypothesis == "X by age",
    country == "World"
  ) %>% 
  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
  select(
    Predictor = predictor, Outcome = outcome, result
  ) %>% 
  pivot_wider(names_from = Outcome, values_from = result)

# And sexes
sex <- coefs %>% 
  filter(
    outcome %in% oo[1:3],
    Hypothesis == "X by sex",
    country == "World"
  ) %>% 
  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
  select(
    Predictor = predictor, Outcome = outcome, result
  ) %>% 
  pivot_wider(names_from = Outcome, values_from = result)

@@

We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between age and sex. DAU predicted negative experiences more negatively, and MAU positive experiences more positively, for the younger age group than for the older (`r age[1, 3]`, `r age[2, 4]`). Other average age differences were not credibly different from zero at the 95% level. The association between DAU and MAU and well-being was more positive for males than it was for females, across all well-being measures, but the differences were not credibly different from zero. We display the average age- and sex-specific associations in the bottom row of Figure \@ref(fig:fig-forest). Overall, these results indicated that the association between Facebook adoption and well-being was more positive for younger individuals, particularly for negative and positive experiences, and that sex-based differences were much smaller in magnitude and not credibly different from zero.

```{r fig-forest}
#| echo: false
#| include: true
#| fig.height: 9
#| fig.width: 7
#| out.width: "\\textwidth" 
#| fig.env: "figure*"
#| fig.cap: "Within-country associations between daily (left; DAU) and monthly (right; MAU) active Facebook users and life satisfaction (LS), negative experiences (NE), and positive experiences (PE). Units indicate percentage change in outcome as function of percentage increase in within-country centered DAU or MAU. Filled points indicate estimates whose 95\\%CI excludes zero."
tmp <- coefs %>%   
  filter(
    outcome %in% oo[1:3],
    str_detect(Hypothesis, "_")
  ) %>% 
  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
  mutate(
    # outcome = case_when(
    #   outcome == "Life_satisfaction" ~ "LS",
    #   outcome == "Negative_experiences" ~ "NE",
    #   outcome == "Positive_experiences" ~ "PE"
    # ),
    predictor = if_else(
      predictor == "dau",
      "Daily active users",
      "Monthly active users"
      )
  ) %>% 
  mutate(cred = pd >= .975)

tmp %>%
  ggplot() +
  aes(
    x = Mean, 
    y = fct_rev(country), 
    col = Age, 
    fill = interaction(Age, cred, sep = " "), 
    shape = Sex
  ) +
  scale_y_discrete(
    "Country",
    expand = expansion(.015),
    labels = ~str_replace(., "World", "Average")
  ) +
  scale_x_continuous(
    str_glue(
      "Association with per capita Facebook users (95%CI)")
    ,
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_shape_manual(
    values = c(21, 22)
  ) +
  scale_color_brewer(
    "Age", palette = "Set1", aesthetics = c("color")
  ) +
  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI_low, xmax = CI_high),
    size = .15, position = position_dodge2v(.7), 
    show.legend = FALSE
  ) +
  geom_point(
    size = .65, stroke = .45,
    position = position_dodge2v(.7)
  ) +
  facet_nested(
    ~ predictor + outcome, scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(size = 1.5)),
    shape = guide_legend(override.aes = list(size = 1.5))
  ) +
  theme(
    text = element_text(size = 9),
    axis.text.y = element_text(size = rel(0.9), vjust = 0.35),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(
      size = .1, linetype = 2, color = "gray60"
    ),
    legend.position = "bottom", 
    legend.title = element_blank(),
    legend.box.margin = margin(-10, 0, -5, 0, "pt")
  )
```
